Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-05-25 ms.tex
plot comparing 2013 and 2015 data.

>>>>

We compare the 2013 and 2015 data to search for any variability in the absorption lines.
Absorption line variability could be caused by variable disintegration activity of the planet and dusty material that sublimates into gas and absorbs against the stellar spectrum.
We compare the 2013 and 2015 data in Figure \ref{fig:spec2013vs2015}.
\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=1.0\textwidth]{images/subaru/2013_vs_2015/2013_vs_2015_spec.pdf}
\caption{Comparison between the 2013 spectrum and 2015 spectrum of \shStar\ near the Mg I triplet. The two are consistent within the larger noise of the 2013 data.}\label{fig:spec2013vs2015}
\end{centering}
\end{figure*}
